### 2015-05-18 README.Rmd
added cran version badge to readme

[![Build Status](https://api.travis-ci.org/ropensci/taxize.png?branch=master)](https://travis-ci.org/ropensci/taxize)
[![Build status](https://ci.appveyor.com/api/projects/status/6mgc02mkd8j4sq3g/branch/master)](https://ci.appveyor.com/project/sckott/taxize-175/branch/master)
[![Coverage Status](https://coveralls.io/repos/ropensci/taxize/badge.svg)](https://coveralls.io/r/ropensci/taxize)
[![rstudio mirror downloads](http://cranlogs.r-pkg.org/badges/taxize)](https://github.com/metacran/cranlogs.app)

>>>>

[![Build Status](https://api.travis-ci.org/ropensci/taxize.png?branch=master)](https://travis-ci.org/ropensci/taxize)
[![Build status](https://ci.appveyor.com/api/projects/status/6mgc02mkd8j4sq3g/branch/master)](https://ci.appveyor.com/project/sckott/taxize-175/branch/master)
[![Coverage Status](https://coveralls.io/repos/ropensci/taxize/badge.svg)](https://coveralls.io/r/ropensci/taxize)
[![rstudio mirror downloads](http://cranlogs.r-pkg.org/badges/taxize)](https://github.com/metacran/cranlogs.app)
[![cran version](http://www.r-pkg.org/badges/version/taxize)](http://cran.rstudio.com/web/packages/taxize)
